### 2020-02-07 README.Rmd
fix #772 - change vignette setup to have them be pre-built; all live within vignettes/ dir now

[![cran checks](https://cranchecks.info/badges/worst/taxize)](https://cranchecks.info/pkgs/taxize)
[![Build Status](https://travis-ci.org/ropensci/taxize.svg?branch=master)](https://travis-ci.org/ropensci/taxize)
[![Build status](https://ci.appveyor.com/api/projects/status/6mgc02mkd8j4sq3g/branch/master)](https://ci.appveyor.com/project/sckott/taxize-175/branch/master)
[![codecov.io](https://codecov.io/github/ropensci/taxize/coverage.svg?branch=master)](https://codecov.io/github/ropensci/taxize?branch=master)
[![rstudio mirror downloads](http://cranlogs.r-pkg.org/badges/taxize)](https://github.com/metacran/cranlogs.app)
[![cran version](http://www.r-pkg.org/badges/version/taxize)](https://cran.r-project.org/package=taxize)

>>>>

[![cran checks](https://cranchecks.info/badges/worst/taxize)](https://cranchecks.info/pkgs/taxize)
[![Build Status](https://travis-ci.org/ropensci/taxize.svg?branch=master)](https://travis-ci.org/ropensci/taxize)
[![Build status](https://ci.appveyor.com/api/projects/status/6mgc02mkd8j4sq3g/branch/master)](https://ci.appveyor.com/project/sckott/taxize-175/branch/master)
[![codecov.io](https://codecov.io/github/ropensci/taxize/coverage.svg?branch=master)](https://codecov.io/github/ropensci/taxize?branch=master)
[![rstudio mirror downloads](https://cranlogs.r-pkg.org/badges/taxize)](https://github.com/metacran/cranlogs.app)
[![cran version](https://www.r-pkg.org/badges/version/taxize)](https://cran.r-project.org/package=taxize)
